## Import the library
```{r}
library(tidyverse)
library(rtweet)
library(reshape2)
library(dplyr)
library(igraph)
library(glue)
```

## Keys and Token
```{r}
api_key <- 'bX5SuJ9xegEl8GJ5so7dsEtkW'
api_secret_key <- 'JEqIU2YiKp5ONwlhU5ut6TgspMpPRvmmaLkssskCx3pnuDTnVp'
access_token <- '1526771089363582977-3VbQQP5VPp3JVj58VilKWOsUr6SZ2N'
access_secret_token <- 'S5fGPg2614GIYt0IdzLXh1mMnQ3YCbMWzZj4xE8Nxcg8i'
```

## List of most-streamed artistis on Spotify
- Blackpink 
- Justin Bieber
- BTS 
- Marshmello
- Eminem
- Ed Sheeran
- Ariana Grande 
- Taylor Swift
- Billie Eilish
- Katy Perry
- Alan Walker
- Bad Bunny
- Rihanna
- One Direction
- XXXTentacion
- Daddy Yankee
- Maroon 5
- Shakira
- Ozuna
- Bruno Mars

## Basic info of the artists

1. twitter user ID
2. number of followers
3. account registered date 
4. number of tweet?

```{r}
artists <- c('BLACKPINK', 'justinbieber', 'BTS_twt', 'marshmello', 'Eminem', 'edsheeran', 'taylorswift13', 'billieeilish', 'katyperry', 'IAmAlanWalker', 'sanbenito',
             'rihanna', 'onedirection', 'xxxtentacion', 'daddy_yankee', 'maroon5', 'shakira', 'ozuna', 'BrunoMars')

artists2 <- c('FKAtwigs', 'andygrammer', 'c_woodzofficial', 'ohashiTrio', 'sadgirlsloan', 'BeachBunnyMusic', 'CAVETOWN', 'clairo', 'oneruel', 'Olivertree',
              'TessaViolet', 'regrettesband', 'rrr001222', 'halfaliveco', 'Sugababes', 'BANNERSMUSIC', 'alliex', 'beforeyouexit', 'Ruellemusic', 'morguemami')

```

```{r}
# artists_info <- lookup_users(artists, parse = TRUE)
artists2_info <- lookup_users(artists2, parse = TRUE)
```

```{r}
# artists_info <- select(artists_info, c('user_id', 'screen_name', 'followers_count', 'friends_count', 'account_created_at'))
artists2_info <- select(artists2_info, c('user_id', 'screen_name', 'followers_count', 'friends_count', 'account_created_at'))
```

```{r}
# write.csv(artists_info, file = "S:\\Study\\DATA419\\GroupProject\\Twitter\\artists_info.csv")
# write.csv(artists2_info, file = "S:\\Study\\DATA419\\GroupProject\\Twitter\\artists2_info.csv")
```

```{r}
# artists_info <- read.csv("S:\\Study\\DATA419\\GroupProject\\Twitter\\artists_info.csv")
# artists2_info <- read.csv("S:\\Study\\DATA419\\GroupProject\\Twitter\\artists2_info.csv")
glimpse(artists_info)
glimpse(artists2_info)
```

## Get the list of followers 
Get 10,000 first for each artist

```{r}
# Get 10,000 followers for each artist

followers <- artists %>%
  map_df(~get_followers(.x, n = 100000, retryonratelimit = TRUE) %>% 
           mutate(from_account = .x))

# followers2 <- artists2 %>%
#   map_df(~get_followers(.x, n = 10000, retryonratelimit = TRUE) %>% 
#            mutate(from_account = .x))
```

```{r}
for (artist in artists) {
followers <- artist %>% get_followers(n = 50000, retryonratelimit = TRUE)
followers %>% write.csv(glue("S:\\Study\\DATA419\\GroupProject\\Twitter\\{artist}_followers.csv"))
}
```

```{r}
followers <- 'selenagomez' %>% get_followers(n = 50000, retryonratelimit = TRUE)
followers %>% write.csv(glue("S:\\Study\\DATA419\\GroupProject\\Twitter\\selenagomez_followers.csv"))

```
```{r}


# 
# followers %>% write.csv("S:\\Study\\DATA419\\GroupProject\\Twitter\\followers.csv")

followers2 %>% write.csv("S:\\Study\\DATA419\\GroupProject\\Twitter\\followers2_more.csv")
```
 
```{r}
followers2 <- read.csv("S:\\Study\\DATA419\\GroupProject\\Twitter\\followers2.csv")
glimpse(followers2)
```

## Transform the data from long to wide to get a incidence matrix
```{r}
# follower_matirx <- followers %>%
#   mutate(yesno = 1) %>%
#   distinct %>%
#   spread(from_account, yesno, fill = 0)


follower2_matirx <- followers2 %>%
  mutate(yesno = 1) %>%
  distinct %>%
  spread(from_account, yesno, fill = 0)
```

```{r}
follower_matirx %>% write.csv("S:\\Study\\DATA419\\GroupProject\\Twitter\\follower_matirx.csv")
```

```{r}
follower_matirx <- read.csv("S:\\Study\\DATA419\\GroupProject\\Twitter\\follower_matirx.csv")
glimpse(follower_matirx)
```

```{r}
for (i in artists) {
print(followers %>% filter(from_account == i) %>% nrow())
}
```


```{r}
common_followers <- follower_matirx %>% cbind(weight = rowSums(follower_matirx[2:20]))
```

```{r}
#glimpse(common_followers)
common_followers <- common_followers[common_followers$weight > 1, ]
```

```{r}
sample <- common_followers %>% top_n(10) 
sample <- sample[2:20] %>% as.matrix()
network <- graph_from_incidence_matrix(sample)
plot(network, vertex.label = NA)
```
```{r}
set.seed(1)
data <- matrix(sample(0:2, 15, replace=TRUE), nrow=3)
colnames(data) <- letters[1:5]
rownames(data) <- LETTERS[1:3]
```

```{r}
## search for 1000 tweets in English
djt <- search_tweets(q = "realdonaldtrump", n = 1000, lang = "en")
```
